Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-23 journal/article.tex
S: People factors

@@

@@

@@

@@

>>>>

% Engage people broadly

@@

% Change leaders

@@

% Have an agile community

@@

% Align the organization

@@

\subsubsection{People factors}

The transformation did not entirely rely on choices in technology and
management, but also different people factors were given as basis of success.

Choosing people with a disposition towards agile methods was seen as a
requirement for the change to take the right track. Teams are staffed usually
based on technical competences, but considering personality aspects alike was
emphasized for agile teams [P29, P34]. The personality of people was seen as a
key aspect for achieving change [P6]. There was a need for collaborative and
understanding persons who are prepared to discard preconceptions and willing to
try new untested approaches [P6, P29].
% Also, having previous agile experience did not directly imply suitability to
% work in a larga scale agile environment [P34].
% In the beginning of the transformation team members who did not find themselves
% comfortable with the new model were exchanged for better suited persons [P29].
